Morus: Biases in the stream

### 2018-05-03 morusAC.tex
fixed mistake in cyclic shift constants

{\tt StepUpdate} is composed of 5 rounds with similar operations to update
the state $S^t$, in which the additional input $m^t$ is used in rounds 2 to 5, but not in round 1. Each round uses the word-wise left circular shift, which divides a $q$-bit register value into 4 words of $q/4$ bits, and performs left circular shift operation for every $q/4$-bit word. Throughout the paper, we denote the word size by $w$, i.e. $w=32$ for \cipher{MORUS640} and $w=64$ for \cipher{MORUS1280}. The word-wise circular shift constants $b_i$ in round $i$ are defined in Table~\ref{Tbl:rcon}. Besides, the left rotation of a whole $q$-bit register is used. The register-wise circular shift constants are also listed in Table~\ref{Tbl:rcon}.
\begin{table}[!htb]
\centering
\caption{Rotation Constants of MORUS} \label{Tbl:rcon}
\begin{tabular}{c||ccccc|ccccc} \hline
& \multicolumn{5}{c|}{register-wise circular shift} & \multicolumn{5}{c}{word-wise circular shift} \\
                  & \makebox[2em]{$b_0$} & \makebox[2em]{$b_1$} & \makebox[2em]{$b_2$} & \makebox[2em]{$b_3$} & \makebox[2em]{$b_4$} & \makebox[2em]{$b'_0$} & \makebox[2em]{$b'_1$} & \makebox[2em]{$b'_2$} & \makebox[2em]{$b'_3$} & \makebox[2em]{$b'_4$} \\ \hline
\cipher{MORUS640} &  5 & 31 &  7 & 22 & 13 & 32 &  64 &  96 &  64 & 32 \\
\cipher{MORUS1280}& 13 & 46 & 38 &  7 &  4 & 64 & 128 & 192 & 128 & 64 \\ \hline
\end{tabular}
\end{table}
We denote those register-wise and word-wise left circular shift by $x \rotl y$ and $x \rotlxy y$, respectively. (Those are denoted by \texttt{<<<} and \texttt{Rotl\_xxx\_yy} respectively in the \cipher{MORUS} design document.)

>>>>

{\tt StepUpdate} is composed of 5 rounds with similar operations to update
the state $S^t$, in which the additional input $m^t$ is used in rounds 2 to 5, but not in round 1. Each round uses the word-wise left circular shift, which divides a $q$-bit register value into 4 words of $q/4$ bits, and performs left circular shift operation for every $q/4$-bit word. Throughout the paper, we denote the word size by $w$, i.e. $w=32$ for \cipher{MORUS640} and $w=64$ for \cipher{MORUS1280}. The word-wise circular shift constants $b_i$ in round $i$ are defined in Table~\ref{Tbl:rcon}. Besides, the left rotation of a whole $q$-bit register is used. The register-wise circular shift constants are also listed in Table~\ref{Tbl:rcon}.
\begin{table}[!htb]
\centering
\caption{Left Circular-Shift Constants of MORUS} \label{Tbl:rcon}
\begin{tabular}{c||ccccc|ccccc} \hline
& \multicolumn{5}{c|}{word-wise circular shift} & \multicolumn{5}{c}{register-wise circular shift} \\
                  & \makebox[2em]{$b_0$} & \makebox[2em]{$b_1$} & \makebox[2em]{$b_2$} & \makebox[2em]{$b_3$} & \makebox[2em]{$b_4$} & \makebox[2em]{$b'_0$} & \makebox[2em]{$b'_1$} & \makebox[2em]{$b'_2$} & \makebox[2em]{$b'_3$} & \makebox[2em]{$b'_4$} \\ \hline
\cipher{MORUS640} &  5 & 31 &  7 & 22 & 13 & 32 &  64 &  96 &  64 & 32 \\
\cipher{MORUS1280}& 13 & 46 & 38 &  7 &  4 & 64 & 128 & 192 & 128 & 64 \\ \hline
\end{tabular}
\end{table}
We denote those register-wise and word-wise left circular shift by $x \rotl y$ and $x \rotlxy y$, respectively. (Those are denoted by \texttt{<<<} and \texttt{Rotl\_xxx\_yy} respectively in the \cipher{MORUS} design document.)
